metric-learn: Metric Learning Algorithms in Python

### 2020-07-03 metric-learn-jmlr.tex
Updates from Overleaf

% Heading arguments are {volume}{year}{pages}{submitted}{published}{author-full-names}

\jmlrheading{}{}{}{}{}{William de Vazelhes and CJ Carey and Yuan Tang and Nathalie Vauquier and Aur\'elien Bellet}

% Short headings should be running head and authors last names

\ShortHeadings{metric-learn: Metric Learning Algorithms in Python}{de Vazelhes, Carey, Tang, Vauquier and Bellet}
\firstpageno{1}

@@

\author{\name William de Vazelhes \email william.de-vazelhes@inria.fr \\
       \addr INRIA, France
       \AND
       \name CJ Carey \email perimosocordiae@gmail.com \\
       \addr Google LLC, United States
       \AND
       \name Yuan Tang \email terrytangyuan@gmail.com \\
       \addr Ant Financial Services Group, United States
       \AND
       \name Nathalie Vauquier \email nathalie.vauquier@inria.fr \\
       \addr INRIA, France
       \AND
       \name Aur\'elien Bellet \email aurelien.bellet@inria.fr \\
       \addr INRIA, France
       }

\editor{}

@@

\paragraph{Positioning with respect to other packages.} Many metric learning algorithms were originally implemented by their authors in \MATLAB without a common API convention.\footnote{See \url{https://www.cs.cmu.edu/~liuy/distlearn.htm} for a list of \MATLAB implementations.}  In R, the package \texttt{dml} \citep{Tang18} implements several metric learning algorithms with a unified interface but is not tightly integrated with any general-purpose machine learning library. In Python, \texttt{pyDML}\footnote{\url{http://github.com/jlsuarezdiaz/pydml}} contains mainly fully supervised and unsupervised algorithms, while \texttt{pytorch-metric-learning}\footnote{\url{http://github.com/KevinMusgrave/pytorch-metric-learning}} focuses on deep metric learning using the \texttt{pytorch} framework \citep{pytorch}.

@@

The current release of \texttt{metric-learn} (v0.6.0) can be installed from the Python Package Index (PyPI) and conda-forge, for Python 3.6 or later.\footnote{Support for Python 2.7 and 3.5 was dropped in the last release.}
The source code is available on GitHub at \url{http://github.com/scikit-learn-contrib/metric-learn} and is free to use, provided under the MIT license. 
\texttt{metric-learn} depends on core libraries from the SciPy ecosystem: \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn}.
Detailed documentation (including installation guidelines, the description of the algorithms and the API, as well as examples) is available at \url{http://contrib.scikit-learn.org/metric-learn}.
The development is collaborative and open to all contributors through the usual GitHub workflow of issues and pull requests.
Community interest for the package has been demonstrated by its recent inclusion in the \texttt{scikit-learn-contrib} organization which hosts high-quality \texttt{scikit-learn}-compatible projects,\footnote{\url{https://github.com/scikit-learn-contrib/scikit-learn-contrib}} and by its more than 1000 stars and 200 forks on GitHub at the time of writing.
The quality of the code is ensured by a thorough test coverage (97\% as of June 2020).
Every new contribution is automatically checked by a continuous integration platform to enforce sufficient test coverage as well as syntax formatting with \texttt{flake8}. %, which allows easy contribution for incoming developers, which can have their code automatically checked.

>>>>

\usepackage{lastpage}
\jmlrheading{21}{2020}{1-\pageref{LastPage}}{8/19; Revised
7/20}{7/20}{19-678}{William de Vazelhes and CJ Carey and Yuan Tang and Nathalie Vauquier and Aur\'elien Bellet}
\ShortHeadings{metric-learn: Metric Learning Algorithms in Python}{de Vazelhes, Carey, Tang, Vauquier and Bellet}

\firstpageno{1}

@@

\author{\name William de Vazelhes\thanks{Most of the work was carried out while the author was affiliated with INRIA, France.} \email wdevazelhes@gmail.com \\
       \addr Paris Research Center, Huawei Technologies\\
       92100 Boulogne-Billancourt, France
       \AND
       \name CJ Carey \email perimosocordiae@gmail.com \\
       \addr Google LLC, United States
       \AND
       \name Yuan Tang \email terrytangyuan@gmail.com \\
       \addr Ant Group, United States
       \AND
       \name Nathalie Vauquier \email nathalie.vauquier@inria.fr \\
       % \addr INRIA, France
       \name Aur\'elien Bellet \email aurelien.bellet@inria.fr \\
       \addr Magnet Team, INRIA Lille – Nord Europe\\
       59650 Villeneuve d’Ascq, France
       }

\editor{Balazs Kegl}

@@

\paragraph{Positioning with respect to other packages.} Many metric learning algorithms were originally implemented by their authors in \MATLAB without a common API convention.\footnote{See \url{https://www.cs.cmu.edu/~liuy/distlearn.htm} for a list of \MATLAB implementations.}  In R, the package \texttt{dml} \citep{Tang18} implements several metric learning algorithms with a unified interface but is not tightly integrated with any general-purpose machine learning library. In Python, \texttt{pyDML} \citep{pyDML} contains mainly fully supervised and unsupervised algorithms, while \texttt{pytorch-metric-learning}\footnote{\url{http://github.com/KevinMusgrave/pytorch-metric-learning}} focuses on deep metric learning using the \texttt{pytorch} framework \citep{pytorch}.

@@

The current release of \texttt{metric-learn} (v0.6.2) can be installed from the Python Package Index (PyPI) and conda-forge, for Python 3.6 or later.\footnote{Support for Python 2.7 and 3.5 was dropped in v0.6.0.}
The source code is available on GitHub at \url{http://github.com/scikit-learn-contrib/metric-learn} and is free to use, provided under the MIT license. 
\texttt{metric-learn} depends on core libraries from the SciPy ecosystem: \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn}.
Detailed documentation (including installation guidelines, the description of the algorithms and the API, as well as examples) is available at \url{http://contrib.scikit-learn.org/metric-learn}.
The development is collaborative and open to all contributors through the usual GitHub workflow of issues and pull requests.
Community interest for the package has been demonstrated by its recent inclusion in the \texttt{scikit-learn-contrib} organization which hosts high-quality \texttt{scikit-learn}-compatible projects,\footnote{\url{https://github.com/scikit-learn-contrib/scikit-learn-contrib}} and by its more than 1000 stars and 200 forks on GitHub at the time of writing.
The quality of the code is ensured by a thorough test coverage (97\% as of June 2020).
Every new contribution is automatically checked by a continuous integration platform to enforce sufficient test coverage as well as syntax formatting with \texttt{flake8}. %, which allows easy contribution for incoming developers, which can have their code automatically checked.
